### 2023-09-03 paper/sec-results.tex
Add FPF chi2 for stat only to table

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.256  &  2.242   & 2.215   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.360    &   2.332  & 2.311  \\
  $\la \chi^2\ra_{\rm rep}$
  & &   1.194   &    1.187    & 1.169  \\
  \midrule
  \multirow{8}{*}{$\chi^2$}
  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
  & FPF (total)                 &  -  &       &      \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
  $\chi^2$ for datasets grouped by process.
  %
  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------

>>>>

%-----------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \footnotesize
  \renewcommand{\arraystretch}{1.30}
  \begin{tabularx}{\textwidth}{X|l|c|c|c}
  \toprule
  & \multirow{3}{*}{Dataset}
  & \multicolumn{3}{c}{\bf NNPDF4.0 NNLO} \\
  &
  & \multirow{2}{*}{Baseline}
  & \multicolumn{2}{c}{with combined FPF data}  \\
  &
  &
  & Statistical-only  & Statistical + systematics  \\
  \midrule
  $\chi^2$ &  \multirow{4}{*}{Global}  & 1.170 &  1.161  & 1.145  \\
  $\la E_{\rm tr}\ra_{\rm rep}$
  &  &  2.256  &  2.242   & 2.215   \\
  $\la E_{\rm val}\ra_{\rm rep}$
  & & 2.360    &   2.332  & 2.311  \\
  $\la \chi^2\ra_{\rm rep}$
  & &   1.194   &    1.187    & 1.169  \\
  \midrule
  \multirow{8}{*}{$\chi^2$}
  & DIS neutral-current                     &  1.220    &  1.230    &   1.220   \\
  & DIS charged-current                     &   0.904  &   0.942    &  0.913    \\
  & Drell--Yan (inclusive and one-jet) &  1.76   &   1.830    &   1.830   \\
  & Top-quark pair production               &  1.230   &   1.220    &  1.250    \\
  & Single-top production                   &  0.362   &   0.364    &   0.361   \\
  & Inclusive jet production                &  0.957   &  0.963     &   0.942   \\
  & Dijet production                        &  2.030    &    2.010   &   2.010   \\
  & Direct photon production                 &  0.740  &   0.729    &    0.744  \\
  & FPF (total)                 &  -  &   1.192    &      \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small Statistical estimators for the NNPDF4.0 NNLO
  baseline fit, compared to the variants including
  the combined FPF dataset shown in Figs.~\ref{fig:NNPDF40_baseline}
  and~\ref{fig:NNPDF40_lowQ_abs}.
  %
  From top to bottom: total $\chi^2$, average
  over replicas of the training and validation figures of merit
  $\la E_{\rm tr}\ra_{\rm rep}$ and $\la E_{\rm val}\ra_{\rm rep}$,
  average $\chi^2$ over replicas $\la \chi^2\ra_{\rm rep}$,
  $\chi^2$ for datasets grouped by process.
  %
  The last row displays the $\chi^2$ obtained for the combined FPF dataset.
  \label{tab:chi2_nnpdf40_baseline}
}
\end{table}
%--------------------------------------------------------------------------
